Standardized crypto-loans on\\ the Cardano blockchain

### 2021-02-03 papers/actus2021/article.tex
added authors, tidied up listings (to verbatim), removed natwidth.

\begin{document}
\title{Standardized crypto-loans on Cardano blockchain\thanks{Supported by Cardano Foundation.}}
\author{First Author\inst{1}\orcidID{0000-1111-2222-3333} \and
Second Author\inst{2,3}\orcidID{1111-2222-3333-4444} \and
Third Author\inst{3}\orcidID{2222--3333-4444-5555}}
%
\authorrunning{F. Author et al.}
\institute{Princeton University, Princeton NJ 08544, USA \and
Springer Heidelberg, Tiergartenstr. 17, 69121 Heidelberg, Germany
\email{lncs@springer.com}\\
\url{http://www.springer.com/gp/computer-science/lncs} \and
ABC Institute, Rupert-Karls-University Heidelberg, Heidelberg, Germany\\
\email{\{abc,lncs\}@uni-heidelberg.de}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
Crypto-loans are unique and innovative financial instruments that
allow trustless P2P lending, which could provide a safe and convenient
source of liquidity for cryptocurrency holders. In this article, we
explore a smart-contract framework for building standardized crypto-loans
with Marlowe DSL and Algorithmic Contract Types Unified Standards
at its core.

\keywords{cardano \and actus \and blockchain \and finance} 
\end{abstract}

@@

\begin{lstlisting}
-- Definitions/ContractState.hs 
data ContractStatePoly a b = ContractStatePoly  
{  
tmd     :: b  
, nt    :: a  
, ipnr  :: a  
, ipac  :: a  
, feac  :: a  
, fac   :: a  
, nsc   :: a  
, isc   :: a  
, prf   :: ContractStatus  
, sd    :: b  
, prnxt :: a  
, ipcb  :: a  
} deriving (Show)

@@

class RoleSignOps a where
   _r :: ContractRole -> a
\end{lstlisting}

@@

\begin{lstlisting}
if condition 
	then 
		perform_something1()
		continue() 
	else 
		perform_something2 
		continue()
\end{lstlisting}

@@

Marlowe only supports Integers, while ACTUS is expressed in terms
of real numbers. In order to model a real number in such a setup -
we rely on fixed point precision. The algebra looks like this: 
\begin{lstlisting}
(+)   = AddValue
(-)   = SubValue
a * b = Scale (1 % marloweFixedPoint) $ MulValue a b
\end{lstlisting}

@@

\begin{lstlisting}
variableName(name, t) = 
	concat(name, '_', t) 
generateAccessor(name, t) = 
	UseValue variableName(name, t) 
generateSetter(name, t, formula) = 
	Let variableName(name, t) formula 
\end{lstlisting}

@@

\begin{figure} 
\includegraphics[width=0.8\textwidth,natwidth=664,natheight=552]{labs.png}
\caption{Actus Labs - online tool for generating Actus contracts for Marlowe.} 
\label{fig3} 
\end{figure}

@@

\begin{lstlisting}
ContractTerms := sample(qcgenerator) 
Contract := generateMarloweContract(ContractTerms) 
ContractWithAssert := appendAssertion(Contract, assertion) 
runStaticAnalysis(ContractWithAssert)
\end{lstlisting}

>>>>

\begin{document}
\title{Standardized crypto-loans on\\ the Cardano blockchain}%\thanks{Supported by Cardano Foundation.}}

\author{Dmytro Kondratiuk\inst{1}\orcidID{XXXX} \and
				Pablo {Lamela Seijas}\inst{1}\orcidID{0000-0002-1730-1219} \and
                Simon Thompson\inst{1,2}\orcidID{0000-0002-2350-301X}}

\authorrunning{D. Kondratiuk, et al.}

\institute{IOHK, Hong Kong,
\email{dmytro.kondratiuk@iohk.io, pablo.lamela@iohk.io, simon.thompson@iohk.io}  \and
School of Computing, University of Kent, UK,
\email{s.j.thompson@kent.ac.uk}}

%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
Crypto-loans are unique and innovative financial instruments that
allow trustless P2P lending, which could provide a safe and convenient
source of liquidity for cryptocurrency holders. In this article, we
explore a smart-contract framework for building standardized crypto-loans
with Marlowe DSL and Algorithmic Contract Types Unified Standards
at its core.

\keywords{Cardano \and ACTUS \and blockchain \and finance \and Marlowe \and Haskell} 
\end{abstract}

@@

\begin{verbatim}
-- Definitions/ContractState.hs 
data ContractStatePoly a b = ContractStatePoly  
{  
tmd     :: b  
, nt    :: a  
, ipnr  :: a  
, ipac  :: a  
, feac  :: a  
, fac   :: a  
, nsc   :: a  
, isc   :: a  
, prf   :: ContractStatus  
, sd    :: b  
, prnxt :: a  
, ipcb  :: a  
} deriving (Show)

@@

class RoleSignOps a where
   _r :: ContractRole -> a
\end{verbatim}

@@

\begin{verbatim}
if condition 
	then 
		perform_something1()
		continue() 
	else 
		perform_something2 
		continue()
\end{verbatim}

@@

Marlowe only supports Integers, while ACTUS is expressed in terms
of real numbers. In order to model a real number in such a setup -
we rely on fixed point precision. The algebra looks like this: 
\begin{verbatim}
(+)   = AddValue
(-)   = SubValue
a * b = Scale (1 % marloweFixedPoint) $ MulValue a b
\end{verbatim}

@@

\begin{verbatim}
variableName(name, t) = 
	concat(name, '_', t) 
generateAccessor(name, t) = 
	UseValue variableName(name, t) 
generateSetter(name, t, formula) = 
	Let variableName(name, t) formula 
\end{verbatim}

@@

\begin{figure} 
\includegraphics[width=0.8\textwidth]{labs.png}
\caption{Actus Labs - online tool for generating Actus contracts for Marlowe.} 
\label{fig3} 
\end{figure}

@@

\begin{verbatim}
ContractTerms := sample(qcgenerator) 
Contract := generateMarloweContract(ContractTerms) 
ContractWithAssert := appendAssertion(Contract, assertion) 
runStaticAnalysis(ContractWithAssert)
\end{verbatim}
